\begin{frame}
\frametitle{Criteria for the paper selection for this class}
\begin{itemize}
\item Must be from per-reviewed journal.
\item The topic close to (bio)medical engineering and your research topics.
\item Need not be review paper, only original research is accepted.
\item Journal must have impact factor assigned.
\item Ph.D. students of OVGU provide you a help in selecting a decent paper.
\item Their choice of papers for the class is on elearning webpages.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Impact factor list}
\scriptsize{\url{https://jcr.incites.thomsonreuters.com/JCRJournalHomeAction.action}}
\begin{itemize}
\item Measurement of quality of publication is a impact factor of the journal (IF)
\item One needs to compare journal impact factors within particular field
\item Well established per-rewiew process
\item Experts in the field evaluates work of the scientists
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Types of research output}
\begin{itemize}
\item Original research papers
\item Conference paper
\item Review paper
\item Book chapter
\item Patent
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Original research paper}
\begin{itemize}
\item Describing \textbf{own} work of a scientist or group of scientists.
\item Need to be original.
\item Need to advance the scientific field.
\item Published in respected journal
\item Per-reviewed
\item \textbf{Only type of research output accepted for presentations.}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Conference paper}
\begin{itemize}
\item Contribution to the conference on scientific topic
\item Describing \textbf{own} work of a scientist or group of scientists.
\item Need to be original.
\item Typically not Per-reviewed
\item \textbf{Not accepted for presentations in class.}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Review paper}
\begin{itemize}
\item Describing work of other scientists on a topic.
\item Typically on request of journal editor.
\item Need not be original.
\item Typically one author.
\item \textbf{Not accepted for presentations in class.}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Book chapter}
\begin{itemize}
\item Elaborate description of particular topic to the detail
\item Need not contain original research of the author.
\item \textbf{Not accepted for presentations in class.}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Patent}
\begin{itemize}
\item \textbf{Not accepted for presentations in class.}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Example}
\bibentry{Parodi2015}


\pause
Abstract: \textit{
This paper provides an overview of the different areas of application of PET in radiation oncology and discusses the most promising perspectives in the years to come for radiation therapy planning, delivery, and monitoring.}
\pause

\textbf{It is review, not accepted for the class.}
\end{frame}

\begin{frame}
\frametitle{Example}
\bibentry{Raylman2018}

\pause
Abstract: \textit{The purpose of this investigation is to test the basic performance of a new dedicated breast‐PET/CT.}

\pause
\textbf{It is original research, accepted for the class.}
\end{frame}

\begin{frame}
\frametitle{Example}
\bibentry{Su2017}

\pause
\textit{This paper summarizes the fundamental principles, the state of the art development, and challenges of fiber-optic force sensors for MRI-guided interventions and rehabilitation. It provides an overview of MRI-compatible fiber-optic force sensors based on different sensing principles.}

\pause
\textbf{It is review, not accepted for the class.}
\end{frame}


\section{Committees}
\begin{frame}
\frametitle{Formation of committees}
\begin{itemize}
\item Find other 2 people with simmilar scientific interests to form 3 member committee.
\item Each student must be a member of exactly one commitee.
\item In committees find 3-5 papers you would like to offer someone for presentation.
\item You can use suggestions on the course webpage.
\item Ask your suppervisors and teachers what kind of papers you should read.
\item Write commitee proposal.
\end{itemize}
\end{frame}



\begin{frame}
\frametitle{Committee proposal}
\begin{itemize}
\item Must be in pdf.
\item Must contain names of members of the committee.
\item \textbf{Have to contain committe introduction and interests (i.e. signal processing, neural networks, particular journal). Approx. 5 sentences. 
\item Have to contain 3-5 papers to offer others for presentation.
\item Have to contain e-mail to the corresponding commitee member.}
\item Have to be submitted by 16.4.2018 to  \href{mailto:vojtech.kulvait@ovgu.de}{vojtech.kulvait@ovgu.de}.
\end{itemize}

Committees proposals will be published on the course webpage.

\end{frame}

