\section{Summary}
\begin{frame}
\frametitle{Summary of the class assignments}
\begin{itemize}
\item You have formed committees.
\item Workshop for summer presenters is 24.4.2018.
\item Workshop for winter presenters is 30.4.2018.
\item By this date, everybody will know his article and people he or she reviews.
\item You will create your presentation and send it for review (to 25.5.2018)
\item You will review presentations of two other people (to 15.6.2018)
\item You will improve your presentation based on the reviews
\item You will deliver your presentation in the class ... next semester
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Workshop format}
\begin{itemize}
\item Each group will present its committee (5min).
\item Say how many free slots committee alredy have.
\item Say how many students registered for the presentation by committee.
\item Students not registered for the presentation will select their committee.
\item Final pairing is done.
\item Committees apply for the time slot in the class schedule.
\end{itemize}
\end{frame}


\begin{frame}
\frametitle{What if you don't get your committee proposal aproved?}
\begin{itemize}
\item You will get one paper selected by the teacher to present.
\item You will get assigned two presenters to review.
\item You can not get any extra points to your evaluation.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{What if you don't review two works of other students?}
\begin{itemize}
\item You fail the class.
\item Your presentation will be cancelled.
\item You can try next year.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{What if you don't read the paper you present or review}

\textbf{You should consider if you'd like to quit your study.}

\end{frame}
