\begin{frame}
\frametitle{Criteria for the paper selection for this class}
\begin{itemize}
\item Must be from per-reviewed journal.
\item The topic close to (bio)medical engineering and your research topics.
\item Need not be review paper, only original research is accepted.
\item Journal must have impact factor assigned.
\item Ph.D. students of OVGU provide you a help in selecting a decent paper.
\item Their choice of papers for the class is on elearning webpages.
\end{itemize}
\end{frame}

\section{Committees}
\begin{frame}
\frametitle{Formation of committees}
\begin{itemize}
\item Find other 2 people with simmilar scientific interests to form 3 member committee.
\item Each student must be a member of exactly one commitee.
\item In committees find 3-5 papers you would like to offer someone for presentation.
\item You can use suggestions on the course webpage.
\item Ask your suppervisors and teachers what kind of papers you should read.
\item Write commitee proposal.
\end{itemize}
\end{frame}



\begin{frame}
\frametitle{Committee proposal}
\begin{itemize}
\item Must be in pdf.
\item Must contain names of members of the committee.
\item \textbf{Have to contain committe introduction and interests (i.e. signal processing, neural networks, particular journal). Approx. 5 sentences. 
\item Have to contain 3-5 papers to offer others for presentation.
\item Have to contain e-mail to the corresponding commitee member.}
\item Have to be submitted by 16.4.2018 to  \href{mailto:vojtech.kulvait@ovgu.de}{vojtech.kulvait@ovgu.de}.
\end{itemize}

Committees proposals will be published on the course webpage.

\end{frame}
