\section{Presentation delivery}

\begin{frame}
\frametitle{Presentation in class}
\begin{itemize}
\item Presentation time is 20 minutes
\item Discussion for 10 minutes
\item Three presentations for the class
\item Typical class will contain presentations of a single comittee
\item Reviewers will evaluate also final presentation and its delivery
\item Committee members will moderate the class of the commitee
\item Committee is responsible for setting order of presentations in the class
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Best practices}
\begin{itemize}
\item 20 minutes can be coverred by around 15 slides
\item Think about rhetorical situation
\item Consider enrollment into the public speaking course
\item Think about invention, arrangement, style, memory and delivery
\item Presenter should know the paper well and be prepared for a discussion
\item Reviewers should also know the paper well and be prepared as well
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Poor practices}
\begin{itemize}
\item Extensive use of copy/paste might be considered as plagiarism leading to not being clasified
\item Moderate text content of the slides
\item Presentation without illustrations
\item Presentation without introduction or summary
\item Hardly understandable presentations for non experts in the topic
\item Not citing all resources might be considered plagiarism as well
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Evaluation - invention}
\begin{itemize}
      \item{Paper was in the scope of the class and lesson (medical engineering)}
      \item{Paper was sufficiently complex for the class}
      \item{Presentation well addresses also the audience without a deep knowledge of the topic}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Evaluation - arrangement}
\begin{itemize}
      \item{Is the talk structured in the meaningful and logical way?}
      \item{Was the proper introduction to a topic given?}
      \item{Was the proper conclusion given? Were there summarized clearly important parts of the talk?}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Evaluation - style}
\begin{itemize}
      \item{The style of the presentation adds up to the understandability of the topic.}
      \item{Proper incomporation of image/media into the presentation.}
      \item{Meaningful captions of the figures}
      \item{Correct references and citations}
      \item{Use the template of OVGU university.}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Evaluation - memory}
\begin{itemize}
      \item{Presenter was well prepared for the talk and the flow of the presentation was smooth.}
      \item{Free speach without major support of manuscript.}
      \item{Compliance with a duration of 20 minutes (2 min. tolerance).}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Evaluation - delivery}
\begin{itemize}
      \item{Good contact and communication with the audience.}
      \item{Posture towards the audience, proper gestures.}
      \item{Speach clarity, articulation, sufficient speach level.}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Evaluation - discussion/other}
\begin{itemize}
      \item{Was the presentation without factical mistakes?}
      \item{Does the presentation provide correct explanation of the main results of the presented paper?}
      \item{Was the speaker well prepared for the discussion?}
\end{itemize}
\end{frame}


\begin{frame}
\frametitle{Evaluation - feedback and questions}
\begin{itemize}
\item Learn how to ask.
\item Asking in the course is a required activity.
\item Try to help presenter to improve by your questions.
\item Committee members should ask.
\item Reviewers should also give feedback on progress during review process.
\end{itemize}
\end{frame}
